NFC and burnout in teachers - A replication and extension study

### 2022-07-20 Manuscript/Manuscript.Rmd
Update Manuscript.Rmd

### Replication of Grass et al. (2018)
Items were reverse coded according to the scale manuals.
NFC and self-control were computed as the sum scores of the NCS and the SCS, respectively.
*Reduced personal efficacy* was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.
NFC was entered as the independent variable, having a direct and multiple indirect effects on MBI via self-control, reappraisal, and suppression as mediators.
Following Grass et al. [-@Grass2018], bootstrapped confidence intervals with $N=2,000$ replicates <!-- add seed and RNG (likely "Mersenne-Twister" -->w ere computed to account for deviations from normality.
Multiple indices were used to evaluate model fit as recommended by Hu and Bentler [-@Hu1999]: the Chi-square test statistic, which measures the fit compared to a saturated model (small values indicate better fit of predicted and observed covariances), the Comparative Fit Index (CFI), which compares the fit to the baseline model ($CFI>.95$ indicates good fit, but $CFI>.90$ is also commonly used), the Standardized Root Mean Square Residual (SRMR), which compares the residuals of the observed and predicted covariance matrix ($SRMR<.08$ indicates fair fit, $SRMR<.05$ good fit), and the Root Mean Square Error of Approximation (RMSEA), which does the same as the latter but takes degrees of freedom and model complexity into account ($RMSEA<.08$ indicates acceptable fit, $RMSEA<.05$ good fit, $RMSEA<.01$ excellent fit).

>>>>

### Replication of Grass et al. (2018)
Items were reverse coded according to the scale manuals.
NFC and self-control were computed as the sum scores of the NCS and the SCS, respectively.
*Reduced personal efficacy* was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.
NFC was entered as the independent variable, having a direct and multiple indirect effects on MBI via self-control, reappraisal, and suppression as mediators.
Following Grass et al. [-@Grass2018], bootstrapped confidence intervals with $N=2,000$ replicates <!-- add seed and RNG (likely "Mersenne-Twister" --> were computed to account for deviations from normality.
Multiple indices were used to evaluate model fit as recommended by Hu and Bentler [-@Hu1999]: the Chi-square test statistic, which measures the fit compared to a saturated model (small values indicate better fit of predicted and observed covariances), the Comparative Fit Index (CFI), which compares the fit to the baseline model ($CFI>.95$ indicates good fit, but $CFI>.90$ is also commonly used), the Standardized Root Mean Square Residual (SRMR), which compares the residuals of the observed and predicted covariance matrix ($SRMR<.08$ indicates fair fit, $SRMR<.05$ good fit), and the Root Mean Square Error of Approximation (RMSEA), which does the same as the latter but takes degrees of freedom and model complexity into account ($RMSEA<.08$ indicates acceptable fit, $RMSEA<.05$ good fit, $RMSEA<.01$ excellent fit).
